Aspects of RDF Data Constraints in the Social, Behavioural and Economic Sciences

### 2015-04-30 paper/paper7/paper7.tex
evaluation

Table \ref{tab:evaluation-complexity-severity} shows the relation between the complexity and the severity level of all 213 constraints.

@@

\begin{hyp}
More than the 1/2 of the vocabulary constraints are error constraints,
more than 3/4 of the simple constraints are informational constraints, and
complex constraints are either informational or error constraints. 
\end{hyp}

As vocabulary constraints are directly extractable from vocabularies and therefore ensure the syntax and semantics of vocabularies,
violations of vocabulary constraints are more severe than violations caused by simple constraints which are easily defined in addition to vocabulary constraints.
In many cases, complex constraints are also needed to express severe constraints which cannot be expressed by modeling languages.
The relation between complexity and severity shows the importance to develop constraint languages which are enable to express severe complex constraints.

>>>>

Table \ref{tab:evaluation-complexity-severity} shows the relation between the complexity and the severity level of all 213 constraints.
More than 1/2 of the \emph{vocabulary constraints} are \emph{error constraints},
more than 3/4 of the \emph{simple constraints} are \emph{informational constraints}, and
\emph{complex constraints} are to the same extend \emph{informational} or \emph{error constraints}.

@@

\begin{hyp}
The further development of constraint languages should concentrate on how to express complex constraints as 44\% of all complex constraints are also serious ones.
\end{hyp}

As vocabulary constraints are contained within formal specifications of vocabularies and therefore directly ensure their syntax and semantics,
violations of vocabulary constraints are more severe than violations caused by simple constraints which are not part of vocabularies.
In many cases, complex constraints are also needed to express severe constraints which cannot be expressed by modeling languages.
The relation between complexity and severity shows the importance to develop constraint languages which are enable to express severe complex constraints.
